---
title: "TRACTION Meeting"
author: "Lauren Wilner"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:   
  html_document:
    toc: true
    toc_float: true
    toc_depth: 6
    theme: simplex
    df_print: paged
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(lubridate)
library(knitr)
library(ggforce)
library(lwgeom)
library(sf)
library(geosphere)
library(measurements)
library(patchwork)
library(kableExtra)

low_active_thresh <- 500
gps_thresh <- 66

# Plotting function
source("~/repos/rwalkbout/R/bout_plot.R")
source("~/repos/rwalkbout/R/concordance.R")
source("~/repos/rwalkbout/R/get_speed_table.R")


```   

*Per Phil et al's paper: PA bouts were defined as time intervals having accelerometer counts > 500 counts per 30 s epoch (cpe) for at least 7 min, allowing for up to 2 min of epochs below that threshold during the 7 min interval.*
<p>
*Per Steve/Amy/Lauren conversations: We have decided that we will consider something a bout as long as it is at least 5 minutes.*
*NOTE: all of this is done presuming that the accelerometry package processed the accelerometry data the same way/the correct way! I cannot use the package right now and thus cannot confirm this* 
<p>
<p>

### Section 1: Overall Concordance 
```{r concordance, echo=FALSE, include=TRUE, message = FALSE}

merge_data <- get_merge_data()
concordance <- get_concordance_table(merge_data)
kable(concordance, booktabs = T, escape = F) %>% 
  add_indent(c(3:6, 8:11)) %>% 
  group_rows("Walk Bouts", 1, 1) %>% 
  group_rows("Phil/Bumjoon Paper", 2,6) %>% 
  group_rows("Our code", 7,11) %>% 
  gsub("NA", " ", .)

```
<p>
<p>


### Section 2: Bouts that differ due to cumulative versus consecutive low/inactive time counting
<p>
<p>

**ID 10902186**:  
```{r ID 10902186, echo=FALSE, include=TRUE, message = FALSE, fig.width=10, fig.height=10}
id <- 10902186
phil_start_time <- ymd_hms("2008-09-09 07:14:00")
phil_end_time <- ymd_hms("2008-09-09 07:33:00")
w_start_time <- ymd_hms("2008-09-09 07:17:00")
w_end_time <- ymd_hms("2008-09-09 07:35:30")
phil_bout_duration <- 19.5

df <- read.csv(paste0("~/walkbout_csvs/", id, "_gps_acc.csv"))

table <- df %>%
  mutate(epoch_time = ymd_hms(epoch_time)) %>% 
  filter(epoch_time > min(phil_start_time, w_start_time)) %>% 
  filter(epoch_time < max(phil_end_time, w_end_time)) %>% 
  select("epoch_time", "Axis1_epochSum", "Activity", "bout_label", "gps_inlier", 
         "epoch_time", "LATITUDE", "LONGITUDE", "Point_circle_area", "Point_radius", "incomplete_GPS")
bout <- table %>% filter(!(is.na(bout_label)))
bout <- unique(bout$bout_label)
bout_plot(id, gps_thresh, low_active_thresh, table)
# kable(table %>% filter(!is.na(bout_label)))

```


**ID 10704259**: We start a bout at 14:22:00 on an active epoch. We end it at 14:33:30 when there are 4+ periods of inactivity. Phil ends at the same point for the same reason. Phil starts his bout on an active epoch at 14:25 presumably because he had been trying to start bouts before that and hitting his threshold of cumulative low/inactivity. This difference can be attributed to a difference in our implementation of cumulative vs consecutive thresholds for ending a bout and thus for where we begin bouts based on where other bouts end.
```{r ID 10704259, echo=FALSE, include=TRUE, message = FALSE, fig.width=10, fig.height=10}
id <- 10704259
phil_start_time <- ymd_hms("2008-09-10 14:25:00")
phil_end_time <- ymd_hms("2008-09-10 14:33:00")
w_start_time <- ymd_hms("2008-09-10 14:22:00")
w_end_time <- ymd_hms("2008-09-10 14:33:30")
phil_bout_duration <- 9

df <- read.csv(paste0("~/walkbout_csvs/", id, "_gps_acc.csv"))

table <- df %>%
  mutate(epoch_time = ymd_hms(epoch_time)) %>% 
  filter(epoch_time > min(phil_start_time, w_start_time)) %>% 
  filter(epoch_time < max(phil_end_time, w_end_time)) %>% 
  select("epoch_time", "Axis1_epochSum", "Activity", "bout_label", "gps_inlier", 
         "epoch_time", "LATITUDE", "LONGITUDE", "Point_circle_area", "Point_radius", "incomplete_GPS")
bout <- table %>% filter(!(is.na(bout_label)))
bout <- unique(bout$bout_label)
bout_plot(id, gps_thresh, low_active_thresh, table)
# kable(table %>% filter(!is.na(bout_label)))

```


**ID 14427353**: This is the same scenario as above with different starts/stops due to differences in cumulative/consecutive inactivity to end a bout. we are already in a bout when phil starts this one! 
```{r ID 14427353, echo=FALSE, include=TRUE, message = FALSE, fig.width=10, fig.height=10}
id <- 14427353
phil_start_time <- ymd_hms("2009-05-29 13:55:00")
phil_end_time <- ymd_hms("2009-05-29 14:06:00")
w_start_time <- ymd_hms("2009-05-29 13:49:00")
w_end_time <- ymd_hms("2009-05-29 14:06:00")
phil_bout_duration <- 11

df <- read.csv(paste0("~/walkbout_csvs/", id, "_gps_acc.csv"))

table <- df %>%
  mutate(epoch_time = ymd_hms(epoch_time)) %>% 
  filter(epoch_time > min(phil_start_time, w_start_time)) %>% 
  filter(epoch_time < max(phil_end_time, w_end_time)) %>% 
  select("epoch_time", "Axis1_epochSum", "Activity", "bout_label", "gps_inlier", 
         "epoch_time", "LATITUDE", "LONGITUDE", "Point_circle_area", "Point_radius", "incomplete_GPS")
bout <- table %>% filter(!(is.na(bout_label)))
bout <- unique(bout$bout_label)
bout_plot(id, gps_thresh, low_active_thresh, table)
# kable(table %>% filter(!is.na(bout_label)))

```

\pagebreak


### Section 2: Differences based on speed 

*PA bouts occurring within a single location were considered as “dwells,” which were considered non-walking by definition. Identifying a dwell bout was accomplished by (1) calculating the sum of distances from each point to all other points within the bout; (2) selecting points having sum distance below the 95th percentile of the sum distances of all points in the bout; (3) generating a minimum bounding circle fully containing the selected points; (4) finally obtaining the circle’s radius. Bouts with radii <= 66 ft were considered as dwell bouts. Because some non-dwell bouts with few GPS observations were likely to have radii <= 66 ft, dwell bouts were defined as having >=10 GPS points.*
<p>
*Three types of issues to look into, will look at 2 of each:* 
*1. Phil identifies a dwell bout and Weipeng identifies nothing* 
*2. Phil identifies a dwell bout and Weipeng identifies a walk bout* 
*3. Phil identifies a dwell bout and Weipeng identifies a nonwalk2_gps_speed bout* 
<p>

```{r speed, echo=FALSE, include=TRUE, message = FALSE}
speed_table <- get_speed_table(merge_data)
speed_table_small <- speed_table %>% 
  group_by(speed_flag) %>% 
  summarise(count = sum(count),
            percent = sum(percent)) %>% 
  arrange(percent)
bar <- ggplot(data = speed_table_small, aes(x = reorder(speed_flag, -percent), y = percent, fill = percent)) + 
  geom_bar(stat="identity") + 
  theme(axis.text.x = element_text(angle = 15)) + 
  labs(xlab = "Speed Metric Equivalencies",
       ylab = "Percent of Total",
       Title = "Distribution of Speed Differences")

speed_table_small <- speed_table_small %>% 
  arrange(speed_flag) %>% 
  rename("Speed Metric Equivalencies" = speed_flag, "Count" = count, "Percent of Total" = percent)

speed_table <- speed_table %>% 
  arrange(speed_flag) %>% 
  rename("Walk Type (our code)" = walk_type.w, "Walk Type (Phil/Bumjoon code)" = walk_type.p, 
         "Speed Metric Equivalencies" = speed_flag, "Count" = count, "Percent of Total" = percent) 

kable(speed_table_small) %>% kable_styling()
kable(speed_table) %>% kable_styling()


```


\bigskip
\pagebreak

#### Code Appendix

```{r, ref.label=knitr::all_labels(),echo=TRUE,eval=FALSE}
```












